FoRTE baseline

### 2019-04-23 analysis/paper/paper.Rmd
Clean up summary time series output

- Summary:
    - Time series of aggregate variables (GPP, NPP, AGB, Total LAI), with error bars by structure
- Structural uncertainty details
    - Understory light environment and how it affects species matters
    - The multiple-scatter
        - Fig: RTM comparison (Radiation profile)
        - Fig: Crown model comparison
        - Fig: Trait plasticity?
- Uncertainty analysis
    - Which parameters contribute the most uncertainty?
    - Structural vs. parameteric uncertainty

>>>>

## Summary

- Time series of aggregate variables (GPP, NPP, AGB, Total LAI), with error bars by structure

```{r summary-captions}
summary_ts_cap <- paste(
  "ED2 plot-level predictions by model configuration."
)
```

```{r summary-ts-plot, fig.cap = summary_ts_cap, fig.dim = c(10, 7)}
readd(summary_ts_plot)
```

## Structural uncertainty details

- Understory light environment and how it affects species matters
- The multiple-scatter
    - Fig: RTM comparison (Radiation profile)
    - Fig: Crown model comparison
    - Fig: Trait plasticity?

## Uncertainty analysis

- Which parameters contribute the most uncertainty?
- Structural vs. parameteric uncertainty
